\center \fontsize{18.8}{20} \selectfont Towards Globally Color-Dual All-Loop Integrands

### 2023-08-29 notes/2loopNLSM.tex
Added some more blurbs in DC and YM.

With a cubic color-dual pion representation in hand, we can perfrom
double copies with many theories to extract ``gravitational''
amplitudes.  Such double-copy constructions are important nontrivial
checks on the underlying single-copy theories: the Jacobi relations in
the single copy conspire to produce the double-copy theory's version
of ``diff. invariance'' \citepls{}.  With pions as one of our single
copies, we will look at producing numerators for special Gallileons,
Born-Infeld theory, and DBIVA by double-copying against pions,
$\mathcal{N}=0$ YM, and $\mathcal{N}=4$ sYM respectively \citepls{}.
These output theories were recently studied extensively by one of the
authors and Carrasco from the perspective of direct unitarity cut
construction \cite{Carrasco:2023qgz}.  One of the shared features of
these 3 theories is that they all have the same physical cut
topologies in 4D: the two diagrams shown in \cref{fig:emu} which are
only composed of even-point amplitudes.

>>>>

With a cubic color-dual pion representation in hand, we can perfrom
double copies with many theories to extract ``gravitational''
amplitudes.  Such double-copy constructions are important nontrivial
checks on the underlying single-copy theories: the Jacobi relations in
the single copy conspire to produce the double-copy theory's version
of ``diff. invariance'' \citepls{}.  With pions as one of our single
copies, we will look at producing numerators for special Gallileons,
Born-Infeld theory, and DBIVA by double-copying against pions,
$\mathcal{N}=0$ YM, and $\mathcal{N}=4$ sYM respectively \citepls{}.
These output theories were recently studied extensively by one of the
authors and Carrasco from the perspective of direct unitarity cut
construction \cite{Carrasco:2023qgz}.  One of the shared features of
these 3 theories is that they all have the same physical cut
topologies in 4D: the two diagrams shown in \cref{fig:emu}, which are
only composed of even-point amplitudes.

To construct the double-copy theories, we source the cubic
$\mathcal{N}=0$ YM numerators from Ref.~\cite{Bern:2015ooa} (which
additionally satisfies a relaxed form of color-kinematics duality),
and the cubic $\mathcal{N}=4$ sYM representation from the well-known
$n_{\text{DB}} = n_{\text{CB}} = s (st\, A_{\text{tree}})$ \citepls{}.

Using the methods of Ref.~\cite{Carrasco:2023qgz}, we can directly
compute the needed basis cuts in all 3 theories without relying on a
color-dual pion representation.
